Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-18 nips_2018.tex
Alignment and stuff
Some work on the table

We apply \system to three domains:
list processing; text editing (in the style of FlashFill~\cite{gulwani2011automating}); and symbolic regression.
 For each of these we initially provide a generic
 set of programming primitives.
Our algorithm then constructs
its own DSL for expressing solutions in the domain (Tbl.~\ref{initialExampleDSL}).
\begin{table}[hb]
\makebox[\textwidth][c]{
  \scriptsize
  \tabcolsep=4pt
\renewcommand\code\texttt
\renewcommand\codechar[1]{\texttt{"#1"}}
\newcommand{\helpSize}{0.25cm}
\begin{tabular}{>{\hspace{-1em}}c<{\hspace{-1em}}>{\hspace{-1em}}c<{\hspace{-1em}}>{\hspace{-1em}}c<{\hspace{-1em}}}\toprule
  {\normalsize List Functions}&{\normalsize Text Editing}&{\normalsize Symbolic Regression}\\\midrule
  {  \tabcolsep=4pt \begin{tabular}{cc}
  \begin{tabular}{c}
      \code{[7\, 0\, 2]}$\to $\code{[2\, 0\, 7]} \\
      \code{[2\, 4\, 9\, 3]}$\to $\code{[3\, 9\, 4\, 2]}\\
      \code{$f(x) = $}\code{($f_0$ nil $x$)}\\\\
      \code{[2\, 7\, 8\, 1]}$\to $\code{8}\\
      \code{[3\, 19\, 14]}$\to $\code{19}\\
      \code{$f(\ell) = $}\code{($f_0$ $\ell$)}
      %% \code{[1]}$\to $\code{[1\, 3]}\\
      %% \code{[7\, 14\, 9]}$\to $\code{[7\, 14\, 9\, 3]}\\
      %% \code{$f(\ell) = $}\code{($f_1$ $\ell$ 3)}\\\\
  \end{tabular}&
  \begin{tabular}{c}
          \code{[7\, 3]}$\to $\code{\#f}\\
          \code{[9\, 4\, 4]}$\to $\code{\#t}\\
          \code{[]}$\to $\code{\#f}\\
          \code{[4\, 7\, 3]}$\to $\code{\#t}\\
      \code{$f(\ell) = $}\code{($f_2$ $\ell$ 4)}
    \end{tabular}
  \end{tabular}}
  &
  \begin{tabular}{c}
    +106 769-438$\to $106.769.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
    +83 973-831$\to $83.973.831\\
    $f(\text{\code{s}}) = $\code{(}$f_0$\code{  \codechar{.} \codechar{,} }\\
    \hspace{1cm}\code{($f_0$ \codechar{.} \codechar{ } (cdr s)))}\\\\
Temple Anna H $\to $TAH\\
Lara Gregori$\to $LG\\
$f(\text{\code{s}}) = $\code{(}$f_2$\code{ s)}\\

  \end{tabular}&

  \begin{tabular}{cc}
    \includegraphics[width = 3em]{figures/functions/4.png}&
    \includegraphics[width = 3em]{figures/functions/146}\\
    \code{$f($x$) = $($f_1$ x)}&    \code{$f($x$) = $($f_6$ x)}\\
    \includegraphics[width = 3em]{figures/functions/112.png}&
        \includegraphics[width = 3em]{figures/functions/92.png}
    \\
    \code{$f($x$) = $($f_4$ x)}&    \code{$f($x$) = $($f_3$ x)}\\

    \end{tabular}

  \\\midrule

  \begin{tabular}{l}
    % $f_0($\code{r}$,\ell) \,=\, $\code{(foldr $\ell$ r ($\lambda$ (x a)}\\
    % \phantom{$f_0($\code{r}$,\ell) \,=\, $\code{(foldr}}\code{(cons (index (length a) $\ell$) a)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number})\\
    % $f_0(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\\hspace{0.8cm}\code{ (if (> a x) a x)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number in $\ell$})\\
    %NOTE: this is the actual invention, but I removed a redundant lambda
    % below: $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ ($\lambda$ (x a) (cons x a)))}\\
    $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}\\
    \vspace{2ex}
      \hspace{\helpSize}($f_0$: \emph{Append lists }\code{r}\emph{ and  $\ell$})\\
    $f_1(\ell,$\code{k}$) \,=\, $\code{($f_0$ (cons k nil) $\ell$)}\\
    \vspace{2ex}
      \hspace{\helpSize}($f_1$: \emph{Append }\code{k}\emph{ to $\ell$})\\
    $f_2(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (is-nil $\ell$)}\\
    \phantom{$f_1(\ell,$\code{k}}
    \code{($\lambda$ (x a) (if a a (= k x))))}\\
      \hspace{\helpSize}($f_2$: \emph{Whether $\ell$ contains }\code{k})\\
  \end{tabular}&

  \begin{tabular}{l}
          $f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map ($\lambda$ (x)}\\\hspace{1cm}\code{ (if (= x a) b x)) s)}\\
      \hspace{\helpSize}($f_0$: \emph{Performs character substitution)}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a)}\\\hspace{1.1cm}\code{ (cdr (if (= c x) s a))))}\\
        \hspace{\helpSize}($f_1$: \emph{Drop characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      $f_2($\code{s}$) \,=\, $\code{(unfold s is-nil car }\\\hspace{1cm}\code{($\lambda$ (z) (}$f_1$\code{ z \codechar{ })))}\\
        \hspace{\helpSize}($f_2$: \emph{Abbreviates a sequence of words})\\
    \end{tabular}&

>>>>

We apply \system to three domains:
list processing; text editing (in the style of FlashFill~\cite{gulwani2011automating}); and symbolic regression.
 For each of these we initially provide a generic
 set of programming primitives.
Our algorithm then constructs
its own DSL for expressing solutions in the domain (Tbl.~\ref{initialExampleDSL}).
\begin{table}[hb]
  \makebox[\textwidth][c]{
    \scriptsize
  \tabcolsep=4pt
  \renewcommand\code\texttt
  \renewcommand\codechar[1]{\texttt{"#1"}}
  \newcommand{\helpSize}{0.25cm}
  \begin{tabular}{>{\hspace{-1em}}c<{\hspace{-1em}}>{\hspace{-2.5em}}c<{\hspace{-0.8em}}>{\hspace{-1em}}c<{\hspace{-1em}}}
    \toprule
    {\normalsize List Functions}&{\normalsize Text Editing}&{\normalsize Symbolic Regression}\\\midrule
    {\tabcolsep=4pt
      \begin{tabular}{cc}
        \begin{tabular}{c}
          \code{[7\, 0\, 2]}$\to $\code{[7\, 0\, 2\, 4]}         \\
          \code{[2\, 4\, 9\, 3]}$\to $\code{[3\, 9\, 4\, 2\, 4]} \\
          \code{$f(x) = $}\code{($f_0$ nil $x$)}             \\
          ~                                                  \\
          ~                                                  \\
          \code{[2\, 7\, 8\, 1]}$\to $\code{8}               \\
          \hspace{0.15cm}\code{[3\, 19\, 14]}$\to $\code{19}                \\
          \code{$f(\ell) = $}\code{($f_0$ $\ell$)}
        \end{tabular}
        &
        \hspace{-0.3cm}\begin{tabular}{c}
          \code{[7\, 3]}$\to $\code{False}                              \\
          \hspace{0.3cm}\code{[3]}$\to $\code{False}                    \\
          \hspace{-0.3cm}\code{[9\, 4\, 4]}$\to $\code{True\phantom{e}} \\
          \hspace{0.3cm}\code{[4]}$\to $\code{True\phantom{e}}                        \\
          \hspace{-0.3cm}\code{[4\, 7\, 3]}$\to $\code{True\phantom{e}}                \\
          \code{$f(\ell) = $}\code{($f_2$ $\ell$ 4)}
        \end{tabular}
      \end{tabular}
    }
    &
    \hspace{-0.5cm}\begin{tabular}{c}
      +106 769-438$\to $106.769.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
      +83 973-831$\to $83.973.831\\
      $f(\text{\code{s}}) = $\code{(}$f_0$\code{  \codechar{.} \codechar{,} }\\
      \hspace{1.25cm}\code{($f_0$ \codechar{.} \codechar{ }}\\
      \hspace{1.4cm}\code{(cdr s)))}\\
      ~\\
      Temple Anna H $\to $TAH\\
      Lara Gregori$\to $LG\\
      $f(\text{\code{s}}) = $\code{(}$f_2$\code{ s)}\\
    \end{tabular}
    &
    \begin{tabular}{cc}
      \includegraphics[width = 3em]{figures/functions/4.png}&
      \includegraphics[width = 3em]{figures/functions/146}\\
      \code{$f($x$) = $($f_1$ x)}&    \code{$f($x$) = $($f_6$ x)}\\
      ~\\
      \includegraphics[width = 3em]{figures/functions/112.png}&
        \includegraphics[width = 3em]{figures/functions/92.png}
      \\
      \code{$f($x$) = $($f_4$ x)}&    \code{$f($x$) = $($f_3$ x)}\\

    \end{tabular}
    ~\\
    \midrule
    \hspace{1cm}\begin{tabular}{l}
      % $f_0($\code{r}$,\ell) \,=\, $\code{(foldr $\ell$ r ($\lambda$ (x a)}\\
      % \phantom{$f_0($\code{r}$,\ell) \,=\, $\code{(foldr}}\code{(cons (index (length a) $\ell$) a)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number})\\
      % $f_0(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\\hspace{0.8cm}\code{ (if (> a x) a x)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number in $\ell$})\\
      %NOTE: this is the actual invention, but I removed a redundant lambda
      % below: $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ ($\lambda$ (x a) (cons x a)))}\\
      $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}\\
      \vspace{2ex}
      \hspace{\helpSize}($f_0$: \emph{Append lists }\code{r}\emph{ and  $\ell$})\\
      $f_1(\ell,$\code{k}$) \,=\, $\code{($f_0$ (cons k nil) $\ell$)}\\
      \vspace{2ex}
      \hspace{\helpSize}($f_1$: \emph{Append }\code{k}\emph{ to $\ell$})\\
      $f_2(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (is-nil $\ell$)}\\
      \phantom{$f_1(\ell,$\code{k}}
      \code{($\lambda$ (x a) (if a a (= k x))))}\\
      \hspace{\helpSize}($f_2$: \emph{Whether $\ell$ contains }\code{k})\\
    \end{tabular}&

  \hspace{0.5cm}\begin{tabular}{l}
    $f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map ($\lambda$ (x)}\\\hspace{1cm}\code{ (if (= x a) b x)) s)}\\
      \hspace{\helpSize}($f_0$: \emph{Performs character substitution)}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a)}\\\hspace{1.1cm}\code{ (cdr (if (= c x) s a))))}\\
        \hspace{\helpSize}($f_1$: \emph{Drop characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      $f_2($\code{s}$) \,=\, $\code{(unfold s is-nil car }\\\hspace{1cm}\code{($\lambda$ (z) (}$f_1$\code{ z \codechar{ })))}\\
        \hspace{\helpSize}($f_2$: \emph{Abbreviates a sequence of words})\\
  \end{tabular}&
